---
title: "Gonfig: Glue + Config"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Gonfig_quick_start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **gonfig** package makes it easy to manage project-wide configuration.

You can install the **gonfig** package from github as follow:

```{r, eval = FALSE}
library(devtools)
devtools::install_github("supermayo/gonfig")
```

## Usage

The usage is the same as [config](https://CRAN.R-project.org/package=config/vignettes/introduction.html) except that it allows [glue](https://glue.tidyverse.org/) litterals.

For instance your config file could be:

***config.yml***
```yaml
default:
  year: 2000
  datafolder: "data"
  clean:
    input: "{datafolder}/data_{year}.csv"
    output: "{datafolder}/clean_{year}.csv"
  predict:
    input: "{clean$output}"
    output: "{datafolder}/forecast_{year+1}.csv"
```

Then you can load the configuratin as a list in R:

```{r, eval = FALSE}
config <- config::get()
config$clean$output
#> "data/data_2000.csv"
config$predict$input
#> "data/forecast_2001.csv"
```

You can load a sub-element from the configuration as follows:

```{r, eval = FALSE}
config <- config::get("predict")
config$input
#> "data/clean_2000.csv"
```


## See Also

Gonfig is pretty much just a wrapper around [config](https://CRAN.R-project.org/package=config/vignettes/introduction.html) and [glue](https://glue.tidyverse.org/). So check their documentation for advanced usage.
